ProbabilityBoundsAnalysis.jl:\\ Arithmetic with sets of distributions

### 2021-10-07 paper/paper.tex
update name

We are also specially grateful to the researchers at JuliaReach and JuliaIntervals, who through their interest, contributions, discussions and suggestions have greatly improved the software: Marcello Forets, Christian Schilling, Luis Benet and David P. Sanders.

>>>>

We are also specially grateful to the researchers at JuliaReach and JuliaIntervals, who through their interest, contributions, discussions and suggestions have greatly improved the software: Marcelo Forets, Christian Schilling, Luis Benet and David P. Sanders.
